\documentclass[12pt,oneside]{article}

\usepackage{amsmath}
\usepackage{enumerate}

\begin{document}
\noindent Name: Kevin Peng \\
Athena username: kpeng94\\
Teammates: Anubhav Jain (ajain94), Kulpreet Chilana (kulpreet)\\
Reflection\\

I think my team worked fairly well together. At the end of our project, we had a working music player that was able to synchronize lyrics with the music and play multiple different voices. I believe we implemented all features correctly, so I think that as a team, we can be proud of our product. In my opinion, the programming was rather straightforward provided that we formally conceptually planned out the implementation. Every member of the team worked together to reason out how the grammar, listener, and abstract data type would be implemented.

Personally, I think I made significant contributions to the team. I wrote the code for the grammar, listener, and part of the abstract data type, specs for the listener and tests for parsing music files. I also helped with editing the design document, transcribed two extra pieces and one of the sample pieces for the first demo. I feel that while I did a large amount of programming the actual implementation of our system, I was able to get through it relatively quickly (and with not too much time spent on actual debugging) because as a team, we made sure that the implementation made sense to all of us before I wrote the code.

Overall, for our team, figuring out how to write the grammar for the parser was pretty difficult. The reasons for this were that we did not come in with much of a background in music. I personally enjoyed gaining the experience of learning some fundamentals in music and combining it with the tools that we learned in 6.005.

\end{document}
